Enzo+Moray: Radiation Hydrodynamics Adaptive Mesh Refinement Simulations with Adaptive Ray Tracing

### 2010-11-16 mnras.tex
Fixed margins, added SVG version of covering factor figure, clarified the "change in incident radiation" timestep method, moved resolution tests to its original position.

\documentclass[useAMS,usenatbib]{mn2e}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{natbib}
%\usepackage[section] {placeins}
\bibliographystyle{mn2e}
\citestyle{mn2e}

@@

\input macros.tex

@@

In this paper, we present our implementation, Enzo+Moray, of adaptive
ray tracing \citep{Abel02_RT} in the cosmological hydrodynamics
adaptive mesh refinement (AMR) code, \enzo~\citep{BryanNorman1997,
  OShea2004}.  The radiation field is coupled to the hydrodynamics
solver at small timescales, enabling it to study radiation
hydrodynamical problems.  We have used this code to investigate the
growth of an \hii region from a 100\Ms~Population III (Pop III) star
\citep{Abel07}, the early stages of reionization from Pop III stars
\citep{Wise08_Reion}, radiative feedback on the formation of high
redshift dwarf galaxies \citep{Wise08_Gal}, ultraviolet radiation
escape fractions from dwarf galaxies before reionization
\citep{Wise09}, negative radiative feedback from accreting Pop III
seed black holes \citep{Alvarez09}, and radiative feedback in
accreting supermassive black holes \citep[][in prep.]{Kim11}.  We have
included Enzo+Moray in the latest public release of
\enzo\footnote{http://enzo.googlecode.com}, and it is also coupled
with the newly added MHD solver in \enzo~\citep{Wang09}.

@@

\begin{figure}
  \plottwo{fig/covering.eps}{fig/calc_fc.eps}
  \caption{\label{fig:covering} (a) A two-dimensional illustration of
    the overlap between the beam associated with a ray $\gamma$ and a
    computational cell.  The ray has a segment length of $dr$ passing
    through the cell.  The covering area is denoted by dark grey,
    where the full area $(dr \times L_{\rm pix})$ is colored by the
    dark and light grey.  The photo-ionization and photo-heating rates
    should be corrected by this overlap fraction $f_c$.  (b)
    Annotation of quantities used in this geometric correction.}
\end{figure}

@@

The contribution to $k_{\rm ph}$ and $\Gamma_{\rm ph}$ must be
corrected by the covering factor $f_c$ of the pixel with respect to
the cell.  When the pixel is fully contained within the cell face,
$f_c \equiv 1$.  Because the geometry of the pixel can be complex with
curved edges, we approximate $f_c$ by assuming the pixel is square.
The covering factor is thus related to the width of a pixel, $L_{\rm
  pix} = R_0 \, \theta_{\rm pix}$, and the distance from the ray
segment midpoint to the closest cell boundary $D_{\rm c,i}$, which is
depicted in Figure \ref{fig:covering}.  To estimate $f_c$, we first
find the distance $d_{\rm center,i}$ from the midpoint of the ray
segment to the cell center $x_{\rm 0,i}$ in orthogonal directions,
%
\begin{equation}
  \label{eqn:midpoint}
  D_{\rm c,i} = \left| R_{\rm 0,i} + \hat{n}_i\,\frac{dr}{2} - x_{\rm
      0,i} \right|,
\end{equation}
where $R_{\rm 0,i}$ is the distance travelled by the ray in each
orthogonal direction.  The distance to the closest cell boundary is
$D_{\rm edge} = dx/2 - \min_{i=1 \rightarrow 3} (D_{\rm c,i})$.  Thus
the covering factor is related to the square of the ratio between the
$L_{\rm pix}$ and $D_{\rm edge}$ by
%
\begin{equation}
  \label{eqn:fc}
  f_c = \left( \frac{1}{2} + \frac{D_{\rm edge}}{L_{\rm pix}} \right)^2
\end{equation}
One half of the pixel is always contained within the cell, which
results in the factor of 1/2.  Finally we multiply $k_{\rm ph}$ and
$\Gamma_{\rm ph}$ by $f_c$ but leave the absorbed radiation $dP$
untouched because this would underestimate the attenuation of the
incoming radiation.  Using $f_c$ calculated like above, the method is
no longer photon conserving.  In our implementation, we felt that the
spherical symmetry obtained outweighed the loss of photon
conservation.  However we show that there are no perceptible
deviations from photon conservation in \S\ref{sec:test1} and
\S\ref{sec:dx_dep}.

@@

\begin{figure*}
  \epsscale{2}
  \plottwo{fig/dtp_test3noavg.eps}{fig/dtp_test3.eps}
  \epsscale{1}
  \caption{\label{fig:dtsmooth} Radiative transfer adaptive timestep
    in shadowing test (Test 3; \S\ref{sec:test3}) while restricting
    the neutral fraction change to 5\% in the ionization front.  The
    unmodified timestep (left) is slightly more noisy and the minima
    are more prominent than the timestep computed with a running
    average of the last two timesteps (right).  The points show every
    tenth timestep taken into account for the running average.  The
    sawtooth behavior is created by the ionization front advancing
    into the next neutral cell in the overdensity.}
\end{figure*}

@@

\textbf{Reorganize to be more clear!}

Ionization front velocities can approach significant fractions of the
speed of light in steep density gradients and in the early expansion
of the \hii region.  If the ionization front position is
critical to the calculation, the radiation transport timestep can be
derived from an estimate of the ionization front velocity
%
\begin{equation}
  \label{eqn:dt_incident}
  v_{\rm IF}(\mathbf{r}) \approx \frac{F(\mathbf{r})}
  {n_{\rm abs}(\mathbf{r})},
\end{equation}
%
based on the incident radiation field at a particular position.  The
timestep is then chosen so that the ionization front only crosses one
cell per timestep $dt_{\rm P, cell} = dx / v_{\rm IF}$, and the global
timestep is $dt_{\rm P} = \min(dt_{\rm P, cell})$.

To make this approach computationally straightforward, we consider a
spherically symmetric case without recombinations.  Thus all photons
emitted from the source result in an ionization (also see
\S\ref{sec:dt_hi}).  Ultimately in any approach, we are focused on
accurately following the time evolution of the radiation field.  In
this method, we base the timestep directly on the change in radiation
field, the specific intensity, $I/\dot{I}$.  We consider the field
after propagating through the cell, so $I = I_0 \exp(-\tau)$, where
$\tau = n_{\rm H} \sigma dl$ is the optical depth through the cell.
The change in specific intensity is
%
\begin{equation}
  \label{eqn:vifront2}
    \frac{dI}{dt} = I_0 \exp(-\tau) (-\dot{n}_{\rm H} \sigma dl),
\end{equation}
%
which can be expressed in terms of local optical depth and neutral
fraction,
\begin{equation}
  \label{eqn:vifront3}
    \frac{dI}{dt} = -I \frac{\tau \dot{n}_{\rm H}}{n_{\rm H}}.
\end{equation}
%
This results in a local timestep
%
\begin{equation}
  \label{eqn:vifront4}
  dt_P = \frac{I}{|dI/dt|} = C_{\rm RT,cfl} \frac{n_{\rm H}}{\tau \dot{n}_{\rm H}},
\end{equation}
%
where $C_{\rm RT,cfl}$ is a safety factor that restricts the change in
intensity to its inverse.  In practice, we have found that a ceiling
of 3 can be placed on the optical depth, so optically thick cells do
not create a very small timestep.  We still find excellent agreement
with analytical solutions with this approximation.  We show the
accuracy using this timestep method in \S\ref{sec:dt_dep}.

@@

\begin{figure*}
  \epsscale{2}
  \plottwo{fig/test1_ionfrac.eps}{fig/test1_ifront.eps}
  \epsscale{1}
  \caption{\label{fig:test1_ifront} Test 1 (\hii region
    expansion with a monochromatic spectrum of 13.6 eV).  Left:
    Radially averaged profile of neutral (solid) and ionized (dashed)
    fraction at 10, 30, 100, and 500 Myr.  Right: Evolution of the
    calculated (top, dashed) and analytical (top, solid) Str\"{o}mgren
    radius.  The ratio of these radii are plotted in the bottom panel.}
\end{figure*}

@@

\begin{figure*}
  \epsscale{2}
  \plottwo{fig/test2_ionfrac.eps}{fig/test2_neutral.eps}
  \epsscale{1}
  \caption{\label{fig:test2_1} Test 2. (\hii region
    expansion with a $T=10^5$ K blackbody spectrum).  Left:
    Radially averaged profile of neutral (solid) and ionized (dashed)
    fraction at 10, 30, 100, and 500 Myr.  Right: Evolution of the
    average neutral fraction.}
\end{figure*}

@@

In Figure \ref{fig:test2_1}, we show the radially averaged neutral and
ionized fraction at $t = $ 10, 30, 100, and 500 Myr, and the total
neutral fraction of the domain.  Compared with Test 1, the ionization
front is thicker, as expected with the harder spectrum.  The total
neutral fraction decreases to 0.67 over 4$t_{\rm rec} = 500$ Myr,
which is in agreement with the analytical expectation and other codes
in RT06.  In Figure \ref{fig:test2_2}, we show slices of neutral
fraction and temperature through the origin at $t = $ 10 and 100 Myr.
Here one sees the spherically symmetric \hii regions and a smooth
temperature transition to the neutral ambient medium.  In Figure
\ref{fig:test2_3}, we show the ratio of the ionization front radius
$r_{\rm IF}$ in our simulation and $R_s$.  Before $1.5t_{\rm rec}$,
$r_{\rm IF}$ lags behind $R_s$, initially by 10\% and then increases
to $R_s$; however afterwards, this ratio asymptotes to a solution that
is 4\% greater than $R_s$.  This behavior is approximately the median
result in RT06, where this ratio varies between 1 and 1.1, and the
early evolution of $r_{\rm IF}$ is under-predicted by almost all of
the codes.  If we use one energy group with the mean energy (29.6 eV)
of a $T=10^5$ K blackbody, we find that $r_{\rm IF}/R_s$ = 1.08, which
is representative of the codes in the upper range of RT06.

@@

\begin{figure*}
  \epsscale{2}
  \plottwo{fig/test3_HI.eps}{fig/test3_temp.eps}
  \epsscale{1}
  \caption{\label{fig:test3_1} Test 3. (I-front trapping in a dense
    clump and shadowing).  Left panel: Line cut from the point source
    through the middle of the dense clump at $t = 1, 3, 5, 15$ Myr.
    of the average neutral fraction (left) and temperature
    (right) of the clump.}
\end{figure*}

@@

\li Perhaps add more description?

@@

\begin{figure*}
  %\epsscale{1.15}
  \epsscale{2}
  \plottwo{fig/test12_kph}{fig/test12_radial}
  \epsscale{1}
  \caption{\label{fig:test12_kph} Test 12 (Time variations of the
    source luminosity).  Left: Slice of the photo-ionization rate
    \kph~through the origin.  The source has a duty cycle of 0.5 Myr,
    and the box has a light crossing time of 3.3 Myr.  The shells of
    high \kph~originate from radiation that was emitted when the
    source was at its peak luminosity, illustrating the
    time-dependence of the radiative transfer equation.  Right: Radial
    profile \kph~with the inverse square law overplotted.}
  %\epsscale{1}
\end{figure*}

@@

\li Add more description of the problem.

@@

\begin{figure*}
  %\epsscale{1}
  \epsscale{2}
  \plotone{fig/phic_slices}
  \epsscale{1}
  \caption{\label{fig:ang_dep1} Variations in the photo-ionization
    rates for different ray-to-cell samplings $\Phi_c$.  The colormap
    only spans a factor of 3 to enhance the contrast.  In comparison,
    the photo-ionization rate actually spans 4 orders of magnitude in
    this test.}
  %\epsscale{1}
\end{figure*}

@@

\begin{figure*}
  %\epsscale{1.05}
  \epsscale{2}
  \plottwo{fig/nures040}{fig/nures100}
  \epsscale{1}
  \caption{\label{fig:nu_dep} Radial profiles of (clockwise from the
    upper left) density, temperature, radial velocity, and ionized
    fraction for Test 5 with $n_\nu = 1$, 2, 4, 8, and 16 frequency
    bins sampling the $T=10^5$ K blackbody spectrum.  The data are
    shown at $t = 200$ Myr (left) and $t = 500$ Myr (right).  The
    double-peaked structure in the shock only appears with a
    multi-frequency spectrum.  The solution converges at $n_\nu \ge
    4$.}  
  %\epsscale{1}
\end{figure*}

@@

\begin{figure*}
  %\epsscale{1.075}
  \epsscale{2}
  \plottwo{fig/noRP_profiles.eps}{fig/RP_profiles.eps}
  \epsscale{1}
  \caption{\label{fig:rp_profiles} (a) No radiation pressure.
    Radial profiles of (clockwise from top left) density, temperature,
    radial velocity, and neutral fraction.  Time units in the legend
    are in kyr.  (b) Radial profiles with radiation pressure.  The
    momentum transferred to the gas drives out the gas at higher
    velocities than without radiation pressure.  Afterwards the
    central region is under-pressurized, and the gas infalls toward the
    center, as seen at t = 60 kyr.  Then the radiation pressure
    continues to force the gas outwards, increasing gas velocities up
    to 50 km/s.}
  %\epsscale{1}
\end{figure*}

>>>>

\documentclass[useAMS,usenatbib,a4paper]{mn2e}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage[section] {placeins}
\bibliographystyle{mn2e}
\citestyle{mn2e}

@@

\input macros.tex
\voffset=-2cm

@@

In this paper, we present our implementation, Enzo+Moray, of adaptive
ray tracing \citep{Abel02_RT} in the cosmological hydrodynamics
adaptive mesh refinement (AMR) code, \enzo~\citep{BryanNorman1997,
  OShea2004}.  The radiation field is coupled to the hydrodynamics
solver at small timescales, enabling it to study radiation
hydrodynamical problems.  We have used this code to investigate the
growth of an \hii region from a 100\Ms~Population III (Pop III) star
\citep{Abel07}, the early stages of reionization from Pop III stars
\citep{Wise08_Reion}, radiative feedback on the formation of high
redshift dwarf galaxies \citep{Wise08_Gal, Wise10_Gal}, ultraviolet
radiation escape fractions from dwarf galaxies before reionization
\citep{Wise09}, negative radiative feedback from accreting Pop III
seed black holes \citep{Alvarez09}, and radiative feedback in
accreting supermassive black holes \citep[][in prep.]{Kim11}.  We have
included Enzo+Moray in the latest public release of
\enzo\footnote{http://enzo.googlecode.com}, and it is also coupled
with the newly added MHD solver in \enzo~\citep{Wang09}.

@@

\begin{figure}
  \plotone{fig/geo_corr.eps}
  \caption{\label{fig:covering} (a) A two-dimensional illustration of
    the overlap between the beam associated with a ray $\gamma$ and a
    computational cell.  The ray has a segment length of $dr$ passing
    through the cell.  The covering area is denoted by dark grey,
    where the full area $(dr \times L_{\rm pix})$ is colored by the
    dark and light grey.  The photo-ionization and photo-heating rates
    should be corrected by the ratio of these areas, i.e. the overlap
    fraction $f_c$.  (b) Annotation of quantities used in this
    geometric correction.}
\end{figure}

@@

The contribution to $k_{\rm ph}$ and $\Gamma_{\rm ph}$ must be
corrected by the covering factor $f_c$ of the pixel with respect to
the cell.  When the pixel is fully contained within the cell face,
$f_c \equiv 1$.  Because the geometry of the pixel can be complex with
curved edges, we approximate $f_c$ by assuming the pixel is square.
The covering factor is thus related to the width of a pixel, $L_{\rm
  pix} = R_0 \, \theta_{\rm pix}$, and the distance from the ray
segment midpoint to the closest cell boundary $D_{\rm c,i}$, which is
depicted in Figure \ref{fig:covering}.  To estimate $f_c$, we first
find the distance $d_{\rm center,i}$ from the midpoint of the ray
segment to the cell center $x_{\rm 0,i}$ in orthogonal directions,
%
\begin{equation}
  \label{eqn:midpoint}
  D_{\rm c,i} = \left| R_{\rm 0,i} + \hat{n}_i\,\frac{dr}{2} - x_{\rm
      0,i} \right|,
\end{equation}
where $R_{\rm 0,i}$ is the distance travelled by the ray in each
orthogonal direction.  The distance to the closest cell boundary is
$D_{\rm edge} = dx/2 - \max_{i=1 \rightarrow 3} (D_{\rm c,i})$.  Thus
the covering factor is related to the square of the ratio between the
$L_{\rm pix}$ and $D_{\rm edge}$ by
%
\begin{equation}
  \label{eqn:fc}
  f_c = \left( \frac{1}{2} + \frac{D_{\rm edge}}{L_{\rm pix}} \right)^2
\end{equation}
One half of the pixel is always contained within the cell, which
results in the factor of 1/2.  Finally we multiply $k_{\rm ph}$ and
$\Gamma_{\rm ph}$ by $f_c$ but leave the absorbed radiation $dP$
untouched because this would underestimate the attenuation of the
incoming radiation.  Using $f_c$ calculated like above, the method is
no longer photon conserving.  In our implementation, we felt that the
spherical symmetry obtained outweighed the loss of photon
conservation.  However we show that there are no perceptible
deviations from photon conservation in \S\ref{sec:test1} and
\S\ref{sec:dx_dep}.

@@

\begin{figure}
  \plottwo{fig/dtp_test3noavg.eps}{fig/dtp_test3.eps}
  \caption{\label{fig:dtsmooth} Radiative transfer adaptive timestep
    in shadowing test (Test 3; \S\ref{sec:test3}) while restricting
    the neutral fraction change to 5\% in the ionization front.  The
    unmodified timestep (top) is slightly more noisy and the minima
    are more prominent than the timestep computed with a running
    average of the last two timesteps (bottom).  The points show every
    tenth timestep taken into account for the running average.  The
    sawtooth behavior is created by the ionization front advancing
    into the next neutral cell in the overdensity.}
\end{figure}

@@

Ionization front velocities can approach significant fractions of the
speed of light in steep density gradients and in the early expansion
of the \hii region.  If the ionization front position is
critical to the calculation, the radiation transport timestep can be
derived from an estimate of the ionization front velocity
%
\begin{equation}
  \label{eqn:dt_incident}
  v_{\rm IF}(\mathbf{r}) \approx \frac{F(\mathbf{r})}
  {n_{\rm abs}(\mathbf{r})},
\end{equation}
%
based on the incident radiation field at a particular position.
Alternatively, the propagation of the ionization front can be
restricted by limiting the change in specific intensity $I$ to a
safety factor $C_{\rm RT,cfl}$, resulting in a timestep of
%
\begin{equation}
  \label{eqn:vifront1}
  dt_P = C_{\rm RT,cfl} \frac{I}{|dI/dt|}.
\end{equation}
%
We consider the specific intensity after the ray travels through the
cell, so $I = I_0 \exp(-\tau)$, where $\tau = n_{\rm H} \sigma dl$ is
the optical depth through the cell.  The time derivative of $I$ is
%
\begin{equation}
  \label{eqn:vifront2}
  \frac{dI}{dt} = I_0 \exp(-\tau) (-\dot{n}_{\rm H} \sigma dl),
\end{equation}
%
which can be expressed in terms of local optical depth and neutral
fraction,
\begin{equation}
  \label{eqn:vifront3}
    \frac{dI}{dt} = -I \frac{\tau \dot{n}_{\rm H}}{n_{\rm H}}.
\end{equation}
%
$\dot{n}_{\rm H}$ is computed with the same formula as
Eq. \ref{eqn:dtelec}. Substituting in Eq. \ref{eqn:vifront1} gives
%
\begin{equation}
  \label{eqn:vifront4}
  dt_P = C_{\rm RT,cfl} \frac{n_{\rm H}}{\tau \dot{n}_{\rm H}}.
\end{equation}
%
In practice, we have found that a ceiling of 3 can be placed on the
optical depth, so optically thick cells do not create a very small
timestep.  We still find excellent agreement with analytical solutions
with this approximation.  We show the accuracy using this timestep
method in \S\ref{sec:dt_dep}.

@@

\begin{figure}
  \plottwo{fig/test1_ionfrac.eps}{fig/test1_ifront.eps}
  \caption{\label{fig:test1_ifront} Test 1 (\hii region
    expansion with a monochromatic spectrum of 13.6 eV).  Top:
    Radially averaged profile of neutral (solid) and ionized (dashed)
    fraction at 10, 30, 100, and 500 Myr.  Bottom: Evolution of the
    calculated (top, dashed) and analytical (top, solid) Str\"{o}mgren
    radius.  The ratio of these radii are plotted in the bottom panel.}
\end{figure}

@@

\begin{figure}
  \plotone{fig/test2_ionfrac.eps}
  \caption{\label{fig:test2_1a} Test 2. (\hii region expansion with a
    $T=10^5$ K blackbody spectrum).  Radially averaged profile of
    neutral (solid) and ionized (dashed) fraction at 10, 30, 100, and
    500 Myr.}
\end{figure}

\begin{figure}
  \plotone{fig/test2_neutral.eps}
  \caption{\label{fig:test2_1b} Test 2. (\hii region expansion with a
    $T=10^5$ K blackbody spectrum).  Evolution of the average neutral
    fraction.}
\end{figure}

@@

In Figure \ref{fig:test2_1a}, we show the radially averaged neutral
and ionized fraction at $t = $ 10, 30, 100, and 500 Myr, and the total
neutral fraction of the domain in Figure \ref{fig:test2_1b}.  Compared
with Test 1, the ionization front is thicker, as expected with the
harder spectrum.  The total neutral fraction decreases to 0.67 over
4$t_{\rm rec} = 500$ Myr, which is in agreement with the analytical
expectation and other codes in RT06.  In Figure \ref{fig:test2_2}, we
show slices of neutral fraction and temperature through the origin at
$t = $ 10 and 100 Myr.  Here one sees the spherically symmetric \hii
regions and a smooth temperature transition to the neutral ambient
medium.  In Figure \ref{fig:test2_3}, we show the ratio of the
ionization front radius $r_{\rm IF}$ in our simulation and $R_s$.
Before $1.5t_{\rm rec}$, $r_{\rm IF}$ lags behind $R_s$, initially by
10\% and then increases to $R_s$; however afterwards, this ratio
asymptotes to a solution that is 4\% greater than $R_s$.  This
behavior is approximately the median result in RT06, where this ratio
varies between 1 and 1.1, and the early evolution of $r_{\rm IF}$ is
under-predicted by almost all of the codes.  If we use one energy
group with the mean energy (29.6 eV) of a $T=10^5$ K blackbody, we
find that $r_{\rm IF}/R_s$ = 1.08, which is representative of the
codes in the upper range of RT06.

@@

\begin{figure}
  \plottwo{fig/test3_HI.eps}{fig/test3_temp.eps}
  \caption{\label{fig:test3_1} Test 3. (I-front trapping in a dense
    clump and shadowing).  Line cut from the point source through the
    middle of the dense clump at $t = 1, 3, 5, 15$ Myr.  of the
    average neutral fraction (top) and temperature (bottom) of the
    clump.}
\end{figure}

@@

@@

\begin{figure}
  %\epsscale{1.15}
  \plottwo{fig/test12_kph}{fig/test12_radial}
  \caption{\label{fig:test12_kph} Test 12 (Time variations of the
    source luminosity).  Top: Slice of the photo-ionization rate
    \kph~through the origin.  The source has a duty cycle of 0.5 Myr,
    and the box has a light crossing time of 3.3 Myr.  The shells of
    high \kph~originate from radiation that was emitted when the
    source was at its peak luminosity, illustrating the
    time-dependence of the radiative transfer equation.  Bottom:
    Radial profile \kph~with the inverse square law overplotted.}
  %\epsscale{1}
\end{figure}

@@

@@

\begin{figure}
  %\epsscale{1}
  %\epsscale{2}
  \plotone{fig/phic_slices}
  \epsscale{1}
  \caption{\label{fig:ang_dep1} Variations in the photo-ionization
    rates for different ray-to-cell samplings $\Phi_c$.  The colormap
    only spans a factor of 3 to enhance the contrast.  In comparison,
    the photo-ionization rate actually spans 4 orders of magnitude in
    this test.}
  %\epsscale{1}
\end{figure}

@@

\begin{figure}
  %\epsscale{1.05}
  \plottwo{fig/nures040}{fig/nures100}
  \caption{\label{fig:nu_dep} Radial profiles of (clockwise from the
    upper left) density, temperature, radial velocity, and ionized
    fraction for Test 5 with $n_\nu = 1$, 2, 4, 8, and 16 frequency
    bins sampling the $T=10^5$ K blackbody spectrum.  The data are
    shown at $t = 200$ Myr (top) and $t = 500$ Myr (bottom).  The
    double-peaked structure in the shock only appears with a
    multi-frequency spectrum.  The solution converges at $n_\nu \ge
    4$.}
  %\epsscale{1}
\end{figure}

@@

\begin{figure}
  %\epsscale{1.075}
  \plottwo{fig/noRP_profiles.eps}{fig/RP_profiles.eps}
  \caption{\label{fig:rp_profiles} (a) No radiation pressure.
    Radial profiles of (clockwise from top left) density, temperature,
    radial velocity, and neutral fraction.  Time units in the legend
    are in kyr.  (b) Radial profiles with radiation pressure.  The
    momentum transferred to the gas drives out the gas at higher
    velocities than without radiation pressure.  Afterwards the
    central region is under-pressurized, and the gas infalls toward the
    center, as seen at t = 60 kyr.  Then the radiation pressure
    continues to force the gas outwards, increasing gas velocities up
    to 50 km/s.}
  %\epsscale{1}
\end{figure}
